Ancestry linkage in hybrid zones

### 2016-02-08 drafts/hybrid_zone.tex
added ancestry frequency figure

>>>>

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim}
\caption{Frequency of ancestry B at a given genomic and physical position at $\tau=100$. Every line represents a locus some distance $r$ away from the true target of selection, and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a similar simulation with no selection.}\label{alleleFreq_tau100}
\end{figure}
